R Notebook

### 2018-10-21 Report/paper-results.Rmd
Changed the graphs to line

Looking at the progression in distance improvements and error improvements over the course of the experiment, we can see that all conditions show progressive improvement which is only hindered by the switch in the desktop learning condition (see fig. XXX and fig. XXX), but in the Treadmill condition we see constant improvement unobstructed by the environmrnt switch.
```{r}
ggplot(sub_walk_all, aes(learning.condition, min_norm_distance, fill=factor(exp_block_id))) +
  stat_summary(fun.data=mean_cl_normal, position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean, position=position_dodge(width=0.95), geom="bar") +
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID") + guides(fill=F)

ggplot(sub_walk_all, aes(learning.condition, errors, fill=factor(exp_block_id))) +
  stat_summary(fun.data=mean_cl_normal, position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean, position=position_dodge(width=0.95), geom="bar") +
  ylab("Average number of errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID") + guides(fill=F)
```

>>>>

Looking at the progression in distance improvements and error improvements over the course of the experiment, we can see that all conditions show progressive improvement which is only hindered by the switch in the desktop learning condition (see fig. XXX and fig. XXX), but in the Treadmill condition we see constant improvement unobstructed by the environmrnt switch.
```{r}
ggplot(sub_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.5, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1.25, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Learning condition") + guides(fill=F)

ggplot(sub_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.5, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1.25, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Learning condition")
```
